---
title: "PSTAT 131/231 - Homework 1"
Author: "Yuer Hao - 9641044"
output: html_document
date: "2022-10-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS) # For Boston data set
library(tidymodels)
library(ISLR)
```

## Machine Learning Main Ideas

Please answer the following questions. Be sure that your solutions are clearly marked and that your document is neatly formatted.

You don’t have to rephrase everything in your own words, but if you quote directly, you should cite whatever materials you use (this can be as simple as “from the lecture/page # of book”).

### Question 1:

Define supervised and unsupervised learning. What are the difference(s) between them?

ANS: Both supervised and unsupervised learning are types of machine learning. In supervised learning, actual observed values of the outcome are known, and the algorithms are trained using labeled data. Therefore, the objective of supervised learning is to develop the model such that it can forecast the outcome when presented with new data. Unsupervised learning, on the other hand, uses machine learning algorithms on data sets without any actual labeled observations in order to find hidden patterns in the data.

### Question 2:

Explain the difference between a regression model and a classification model, specifically in the context of machine learning.

ANS: In the context of machine learning, the distinction between regression and classification models is that regression models include a continuous outcome whereas classification models contain a categorical outcome.

### Question 3:

Name two commonly used metrics for regression ML problems. Name two commonly used metrics for classification ML problems.

ANS: For regression ML problems, two commonly used metrics are Mean squared error (MSE), and Mean absolute error (MAE).

For classification ML problems, two commonly used metrics are precision and the area under the curve (AUC).


### Question 4:

As discussed, statistical models can be used for different purposes. These purposes can generally be classified into the following three categories. Provide a brief description of each.

ANS:
Descriptive models: used to emphasize a pattern or trends in data visually, for as when a scatterplot is fitted using a linear regression to show a relationship.

Inferential models: used to draw conclusions regarding the relationship(s) that exist between the outcome and the predictor(s). The goal is to find out what is are the significant features and implications for theories.

Predictive models: It is used to predict the best-fitted outcome variable as precisely as feasible while minimizing reducible error; it is not focused on hypothesis testing.

(reference - Lecture: Course Overview and IntroductionFile,P39)



### Question 5:

Predictive models are frequently used in machine learning, and they can usually be described as either mechanistic or empirically-driven. Answer the following questions.

i) Define mechanistic. Define empirically-driven. How do these model types differ? How are they similar?

ANS: 
A mechanistic model makes predictions about the future based on a theory. An  empirically-driven model looks at actual occurrences to build a theory. So they both aim to find trends or patterns.
Mechanistic models assume a parametric form for the relationship between the predictor(s) and the outcome, which will unlikely match the true, unknown form. Adding parameters to mechanistic models will make it more flexible.
Empirically-driven models make little to no assumptions regarding the form of the relationship, and are originally more flexible. 

ii) In general, is a mechanistic or empirically-driven model easier to understand? Explain your choice.

ANS:
Mechanistic models generally fit very basic parametric forms, making them more straightforward to understand.

iii) Describe how the bias-variance tradeoff is related to the use of mechanistic or empirically-driven models.

ANS:
Mechanistic models often have lower variance and higher bias. Empirically-driven models often exhibit less bias and more variance.


### Question 6:

A political candidate’s campaign has collected some detailed voter history data from their constituents. The campaign is interested in two questions:

Given a voter’s profile/data, how likely is it that they will vote in favor of the candidate?

How would a voter’s likelihood of support for the candidate change if they had personal contact with the candidate?

Classify each question as either predictive or inferential. Explain your reasoning for each.

ANS: In the first question, the campaign is centered on figuring out the likelihood of voter behavior, therefore the first question is predictive.
In the second question, the campaign is more interested in the precise relationship between a candidate interaction (predictor), and the voter behavior (outcome), therefore the first question is inferential.

## Exploratory Data Analysis
This section will ask you to complete several exercises. For this homework assignment, we’ll be working with the `mpg` data set that is loaded when you load the tidyverse. Make sure you load the tidyverse and any other packages you need.

Exploratory data analysis (or EDA) is not based on a specific set of rules or formulas. It is more of a state of curiosity about data. It’s an iterative process of:

generating questions about data
visualize and transform your data as necessary to get answers
use what you learned to generate more questions
A couple questions are always useful when you start out. These are “what variation occurs within the variables,” and “what covariation occurs between the variables.”

You should use the tidyverse and `ggplot2` for these exercises.

### Exercise 1:
We are interested in highway miles per gallon, or the `hwy` variable. Create a histogram of this variable. Describe what you see/learn.
```{r E1, echo=TRUE}
mpg %>%
  ggplot(aes(x=hwy)) +
  geom_histogram(bins=30)
```


The distribution of highway mileage shows a positively skewed distribution. Although such distributions are quite uncommon, it also almost seems to have two maximum point; the highest peak is at 26–27 mpg and another around 16–17 mpg. It seems like no vehicles get less than 10 mpg and few vehicles get more than 40 highway miles per gallon.




### Exercise 2:
Create a scatterplot. Put `hwy` on the x-axis and `cty` on the y-axis. Describe what you notice. Is there a relationship between `hwy` and `cty`? What does this mean?

```{r}
mpg %>%
  ggplot(aes(x = hwy, y = cty)) +
  geom_point()
```

Certainly, it appears that the correlation between highway mileage and city mileage are positively linear correlated. It should be noted that the points appear to be organized in a grid-like arrangement. It means that when the hwy increases, the cty will also increase.


### Exercise 3:
Make a bar plot of `manufacturer`. Flip it so that the manufacturers are on the y-axis. Order the bars by height. Which manufacturer produced the most cars? Which produced the least?

```{r}
mpg %>% 
 ggplot(aes(x = forcats::fct_infreq(manufacturer))) +
 geom_bar() +
 coord_flip()
```

Dodge produced the most cars, which is almost 40
Lincoln produced the least car, which is less than 5.


### Exercise 4:
Make a box plot of hwy , grouped by cyl . Do you see a pattern? If so, what?

```{r}
mpg %>% 
 ggplot(aes(x = hwy, y = factor(cyl))) +
 geom_boxplot() +
 xlab("Highway Mileage") +
 ylab("Cylinders")
```

Yes, the highway mileage does tend to decrease as the number of cylinders rises. On average, four-cylinder cars get the highest mileage. The average for five-cylinder automobiles is close, but there are a lot less five-cylinder cars in the data set.


### Exercise 5:
Use the corrplot package to make a lower triangle correlation matrix of the mpg dataset. 

Since there are some categorical variables in the data set, you can decide how to deal with these. One way is simply to exclude them from the plot, which is what is done here.

Which variables are positively or negatively correlated with which others? Do these relationships make
sense to you? Are there any that surprise you?
```{r}
#install.packages("corrplot")
library(corrplot)
mpg %>% 
  select(is.numeric) %>% 
  cor() %>% 
  corrplot(type = "lower")
```


The displ is positively associated withe year and cyl, but negatively associated with cty and hwy. 
The year is negatively associated with cty, but positively associated with hwy and cyl. 
The cyl is negatively associated with cy and hwy.
The cty is positively associated with hwy.

The results make sense and not surprise to me.

### Exercise 6:
Recreate the following graphic, as closely as you can. Hint: Use the ggthemes package.

```{r}
#install.packages("ggthemes")
library(ggthemes)
mpg %>%
 ggplot() +
 geom_boxplot(mapping = aes(x = class, y = hwy)) +
 geom_jitter(mapping = aes(x = class, y = hwy), 
 alpha = .25, 
 height = 0) +
 theme_gdocs() +
 labs(x = "Vehicle Class", y = "Highway MPG") +
 coord_flip()
```

### Exercise 7:

```{r}
mpg %>%
 ggplot() + 
 geom_boxplot(mapping=aes(x = class, y = hwy, fill = drv))
```


### Exercise 8:

```{r}
mpg %>%
 ggplot(mapping = aes(x = displ, y = hwy)) + 
 geom_point(aes(color = drv)) +
 geom_smooth(aes(linetype = drv), se = FALSE, method = 'loess', formula = 'y ~ x')
```